Draft information

### 2020-04-18 paper/draft-info.Rmd
Update draft info
Add ref to manuscript

* Fix a couple of references
* Add a few references to the methods justifying occurrence cleaning approach (thanks Audrey)

@@

* Jason, one of your comments was: *"I can't remember if I've raised this before, but if species are near to the boundaries of number of partners (close to zero or close to N, where N is the number of species in a community), a random change in the number of partners is more likely to bring them towards the mean because they can't go any higher than N or lower than 0. Is there any way to deal with this?"*. That certainly might be happening for species with few partners. I try to address that in the discussion (see \lr{regression-to-the-mean}). I don't think it happens for species with many partners because very few of the species analysed are close to N (only ~2% of plants and ~3% of animals have a normalised degree > 0.5, ~0.5% of both have a normalised degree > 0.75). To avoid confusion I've removed the "regression to the mean" statements in the discussion. 
* Appart from that, I think I followed most suggestions one way or another. **Thanks!**

>>>>

* Add a few references to the methods justifying occurrence cleaning approach (thanks Audrey)

@@

* Jason, one of your comments was: *"I can't remember if I've raised this before, but if species are near to the boundaries of number of partners (close to zero or close to N, where N is the number of species in a community), a random change in the number of partners is more likely to bring them towards the mean because they can't go any higher than N or lower than 0. Is there any way to deal with this?"*. That certainly might be happening for species with few partners. I try to address that in the discussion (see \lr{M-regression-to-the-mean}). I don't think it happens for species with many partners because very few of the species analysed are close to N (only ~2% of plants and ~3% of animals have a normalised degree > 0.5, ~0.5% of both have a normalised degree > 0.75). To avoid confusion I've removed the "regression to the mean" statements in the discussion. 
* Appart from that, I think I followed most suggestions one way or another. **Thanks!**
